---
output:
  pdf_document:
    latex_engine: pdflatex
    citation_package: natbib
    template: mk_Rpackage_template.tex
    toc: true
    toc_depth: 2
    includes:
        in_header: vignette_head.tex
    keep_tex: true
title: "Contamination Bias in Linear Regressions"
author: "Sai Zhang"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 10pt
bibliography: np-testing-library.bib
vignette: >
  %\VignetteIndexEntry{Contamination Bias in Linear Regressions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, cache=FALSE}
library("knitr")
library("formatR")
knitr::opts_knit$set(self.contained = FALSE)
knitr::opts_chunk$set(tidy = TRUE, collapse=TRUE, comment = "#>",
                      tidy.opts=list(blank=FALSE, width.cutoff=55))
```

# Introduction

The package `multeR` implements contamination bias decomposition and bias-aware
estimation for linear regressions considered in @goldsmith2022contamination. 
In this vignette, we demonstrate the implementation using Project STAR data as
in @krueger1999experimental, which are included in the package as a data frame 
`star`.

# Model

```{r}
library(multeR)
```

# Bias-aware treatment effect estimation
```{r, }
multe(score ~ treatment | school, data=star, base_val = "regular")
multe(score ~ treatment | school, data=star, base_val = "regular", vce = "oracle")
```

# Contamination bias decomposition
```{r, }
multe(score ~ treatment | school, data=star, base_val = "regular", decomp = TRUE)
multe(score ~ treatment | school, data=star, base_val = "regular", 
      decomp = TRUE, minmax = TRUE)
```

# Save implicit regression weights and group-specific treatment effects
One can save the implicit ATE regression weights and the saturated group-specific 
treatment effects, then calculate the correlations to get a sense of how much 
contamination bias might affect estimates from such a model.
 
```{r, }
d <- multe(score ~ treatment | school, data=star, base_val = "regular", 
           decomp = TRUE, save_lambda_as = "lambda", save_tau_as = "tau", print=FALSE)
lambda <- d$decomposition$lambda_saved
tau <- d$decomposition$tauhat_saved
cor(lambda,tau)
```

# Weak overlapping
Weak overlapping strata will be dropped, as shown in this pseudo example.
```{r, }
df <- star
df$moc_ctrl <- rep(1:5, length.out=length(df$score))
multe(score ~ treatment | school + moc_ctrl, data=df, base_val = "regular", decomp = T)
```

# Reference
